Capturing underlying musical structure: an audio-based approach using deep learning

### 2023-02-09 MasterThesis.tex
Updates from Overleaf
5-2-2023 commit

\documentclass[a4paper,12pt,twoside]{report}
\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry} %Margins
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{chngcntr }
\usepackage[toc,page]{appendix}
\usepackage[T1]{fontenc}
\usepackage[nottoc]{tocbibind}
\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{1ex}{0ex}
\titlespacing{\subsection}{0pt}{1ex}{0ex}
\titlespacing{\subsubsection}{0pt}{1ex}{0ex}

@@

%Title parameters
\title{Multi-level audio-based music structure analysis}
\author{Oriol Colomé Font}
\submitdate{July 2023}
\supervisor{Carlos Lordelo and Carl Thomé}
\cosupervisor{Frederic Font}

@@

\maketitle
\restoregeometry

\preface
\cleardoublepage 
\input{dedication/dedication}
\input{acknowledgements/acknowledgements}
\input{abstract/abstract}

@@

%Introduction of the project
\input{introduction/introduction}
\input{methods/methods}
\input{results/results}
\input{discussion/discussion}

>>>>

\documentclass[a4paper,12pt,twoside]{report}

\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry} %Margins
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{chngcntr }
\usepackage[toc,page]{appendix}
\usepackage[T1]{fontenc}
\usepackage[nottoc]{tocbibind}
\usepackage[compact]{titlesec}
\usepackage{float}

\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, latexsym}
\usepackage{sidecap}
%---tikz---
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{fadings}

\titlespacing{\section}{0pt}{1ex}{0ex}
\titlespacing{\subsection}{0pt}{1ex}{0ex}
\titlespacing{\subsubsection}{0pt}{1ex}{0ex}

@@

%Title parameters
\title{Capturing underlying musical structure: an audio-based approach using deep learning}
\author{\href{oriol.colome.font@epidemicsound.com}{Oriol Colomé Font}}
\submitdate{July 2023}
\supervisor{Carlos Lordelo and Carl Thomé}
\cosupervisor{Frederic Font}

\hypersetup{
pdftitle={Your PDF title},
pdfsubject={Your PDF subject},
pdfauthor={Oriol Colomé Font},
pdfkeywords={Music; 
Music Theory; 
Music Information Retrieval; 
Music Structure Analysis; 
Machine Learning; 
Neural Networks; 
Deep Learning}
}

@@

%\maketitle
\restoregeometry

\preface
\cleardoublepage 
\input{dedication/dedication}
\input{acknowledgements/acknowledgements}
\input{preface/preface}
\input{abstract/abstract}

@@

%Introduction of the project
\input{introduction/introduction}
%Music analysis explanation
\input{music analysis/MSA}
%Methods
\input{methods/methods}
%Results
\input{results/results}
%Discussion
\input{discussion/discussion}

### 2023-02-09 abstract/abstract.tex
Updates from Overleaf

The abstract should have at least 200 but not more than 600 words. Placed on the right page next to a blank left page. A list of keywords (approximately 3 to 5) should be just below the abstract, preceded by the word "Keywords". Keywords should be separated by ";".

\bigskip
Keywords: Music Information Retrieval; Music Structure Analysis; Deep Learning

>>>>

The abstract should have at least 200 but not more than 600 words. Placed on the right page next to a blank left page.

\bigskip
Keywords: Music; Music Theory; Music Information Retrieval; Music Structure Analysis; Machine Learning; Neural Networks; Deep Learning

### 2023-02-09 introduction/introduction.tex
Updates from Overleaf

As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and the underlying relationship among them. I am deeply interested in learning how to retrieve embedded information within music. The study of music structure analysis provides a means to systematically analyze and understand musical pieces. It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.

>>>>

As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationship among them. I am deeply interested in learning how to retrieve embedded information within music. The study of music structure analysis provides a means to systematically analyze and understand musical pieces. It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.
